\documentclass{article}
\usepackage{ctex}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{physics}
\usepackage[top=2cm, bottom=2cm, left=3cm, right=3cm]{geometry}
\usepackage{graphicx}



\newtheorem{theorem}{定理}
\newtheorem{definition}{定义}
\newtheorem{solution}{解}




\newcommand{\pmtwo}[4]{
    \begin{pmatrix}
        #1&#2\\
        #3&#4
    \end{pmatrix}
    }
\newcommand{\pmthree}[9]{
    \begin{pmatrix}
        #1&#2&#3\\
        #4&#5&#6\\
        #7&#8&#9
    \end{pmatrix}
}
\newcommand{\vmtwo}[4]{
    \begin{vmatrix}
        #1&#2\\
        #3&#4
    \end{vmatrix}
    }
\newcommand{\vmthree}[9]{
    \begin{vmatrix}
        #1&#2&#3\\
        #4&#5&#6\\
        #7&#8&#9
    \end{vmatrix}
}

\newcommand{\expectation}[1]{\langle #1 \rangle}

\newcommand{\Da}[2]{\frac{\partial}{\partial#2}#1}

\newcommand{\D}[2]{\frac{d}{d#2}#1}

\newcommand{\id}[1]{\ket{#1}\bra{#1}}



\title{University of South China Quantum Mechanics
Midterm Exam}
\author{Kaiser}
\date{November 11, 2024}


\begin{document}

\maketitle


\begin{enumerate}
    \item (20 points) If $[A, H] = 0$, $[B, H] = 0$,but $[A, B] \neq 0$, please prove that
    there is degeneracy happened in the system.
    \item (40 points in total) Consider an electron in a box with the potential of the
    box to be defined as:
    $$
        V (x, y, z) =
        \begin{cases}
            0,& 0 \leq  x \leq  L, 0 \leq  y \leq  L, and\ 0 \leq  z \leq  L,\\
            \infty ,&otherwise.
        \end{cases}
    $$
    \begin{enumerate}
        \item (10 points) Please write down the time-dependent Schrödinger equation of the system.
        \item (10 points) Please find out the normalized general solution of the Schrödinger equation and energy spectrum.
        \item (10 points) Please find out the commutation relation between the operators $x$, $y$, $z$,$ p_x$, $p_y$, and $p_z.$
        \item (10 points) By using the ground state solution, please find out theexpectation values $\langle x\rangle$, $\langle x^2\rangle$, $\langle p_x\rangle$,and $\langle p^2_x\rangle$,and check the uncertainty principle.
    \end{enumerate}
    \item (40 points in total) Consider the following potential:
        \[V (x) = 4x^4 − 2L^2x^2 + L^4\]
        \begin{enumerate}
            \item (10 points) In this potential, there are two minimums. Please sketch the potential and find out the position α of the two minimums.
            \item (10 points) Please write down the raising and lowering operators $a_+$ and $a_−$ and work out the commutation relation $[a_+, a_−]$ for the two minimums individually.
            \item (10 points) Please find out the unnormalized ground state solutions and the spectrum of the two minimums.
            \item (10 points) Please find out the commutation relation between the raising and lowering operators and the position $x$.
        \end{enumerate}


\end{enumerate}











\end{document}